### 2019-06-30 thesis.tex
more text

Describing such complicated dynamics it is not an easy task.

>>>>

A complete description of such a complicated dynamics would depend on determining
the position and momentum of each particle, and their respective microscopic
electric and magnetic fields, in a time instant. This strategy is not practical
and in most of the cases not feasible for many-body systems, like the plasma.  
However, this microscopic description can be dealt through a hierarchy of
approximations, leading to the three main theories of plasma physics: kinetic,
multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
formulations will depend on the phenomenon that needs to be described,
